---
output:
  pdf_document: default
  html_document: default
---
**Project aim* AS NTUC can get busy during peak hours, our group wanted to study what is the optimal number of checkout counters such that it will help reduce the waiting time and queue length during peak hours.Therefore, our group has done 5 models, to compare and find out which one is the best model.This project aims to improve mean waiting time and mean queue length by at least 30% from the base model.

**How We collect data* 
From 6pm-8Pm on Sunday
1.Normal and self-checkout counters :Once the customer start scanning the items, we start the timer and once the customer leaves the counter we stop the timer. 

2.Arrival rate: Every min, we count the arrival of customers into NTUC. (we stand at the entrance of NTUC)

**Assumptions for our model*
1.Service rate of counters remains approximately the same throughout the day and on different days.

2.Arrival rate approximately the  same for the other time through the day and for other days

3.No down time for the normal counters and self-checkout counters.

4.No delay when switching of shift at the normal counters and self-checkout counters.

5.Data collected in this branch is approximately the same for the other branches.


**Step 1.**After collecting data, our group went to fit the data and find the best distribution for each parameters

```{r check dist}

library(fitdistrplus)
library(tidyverse)

normal_counter<-c(89,130,108,108,405,91,118,209,210,120,150,45,161,271,59,218,188,109,140,249,253,81,64,137,25,161,105,114,405,133,230) #normal, these in seconds
hist(normal_counter)
normal_counter<-normal_counter/60 #convert to minute

norm_normalcounter <- fitdist(data=normal_counter,distr="norm")
mean<-norm_normalcounter$estimate[1]
sd<-norm_normalcounter$estimate[2]

qqcomp(norm_normalcounter)
denscomp(norm_normalcounter)

selfcheck_counter<-c(115,332,225,308,122,80,118,53,120,74,75,68,52,124,74,101,69,115,73,110,156,48,57,37,80,68,176,79,132,76,103) #exp

hist(selfcheck_counter)

selfcheck_counter<-selfcheck_counter/60

#compare
exp_selfcheck <- fitdist(data=selfcheck_counter,distr="exp")
rate<-exp_selfcheck$estimate[1]

qqcomp(exp_selfcheck)
denscomp(exp_selfcheck)

norm_selfcounter <- fitdist(data=selfcheck_counter,distr="norm")
mean1<-norm_selfcounter$estimate[1]
sd1<-norm_selfcounter$estimate[2]
qqcomp(norm_selfcounter)
denscomp(norm_selfcounter)



arrival<-c(3,4,7,3,4,3,4,5,3,3,5,7,4,3,5,4,3,4,5,4,5,4,3,2,5,4,3,4,5,3,5,7,4,4,5,4,5,5,7,3,2,5,4,7,3,5,6,6,4,8,7,4,5,6,3,4,7,6,4) #poi number of arrival per minute

hist(arrival)

set.seed(1)
observed <- tabulate(arrival) #table when have x=0, 
table(arrival)
names(observed) <- 1:max(arrival)
observed
pois_par <- fitdist(data = arrival, # Use the dummy dataset
                                 distr = "pois") # Select Poisson
(lambda <- pois_par$estimate[1]) # Store value of lambda as lambda

fitted_pois <- dpois(x = 1:max(arrival),
                     lambda = lambda) * sum(observed)
library(vcd)

rootogram(x = observed,
          fitted = fitted_pois,
          type = "hanging",
          main = "Poisson (hanging)")

 
```

**Step 2.** We do a p-value test on the hypothesis h0 = The population mean of the two treatment groups are the same 

```{r p-value test}
set.seed(1)
df1 <- read.csv('../data/project.csv')
original <- mean(df1[1:31,2]) - mean(df1[32:62,2])
original
summary(df1)
treatment <- df1$treatment
treatment
outcome <- df1$outcome
outcome
set.seed(1)
permutation.test <- function(treatment, outcome){
    # Generate a permutation sample
    treatment_p <- sample(treatment, size= length(treatment), replace=FALSE)
    # Calculate the test statistic for the permutation sample
   mean(outcome[treatment_p == "normal"]) - 
                          mean(outcome[treatment_p == "self"]) 
  }

# Slide 22: Use the "replicate()" Function to Run Multiple Simulations
test <- replicate(10000, permutation.test(treatment, outcome))
p_value<-mean(abs(test) >= abs(original))
p_value
#since p-value is less than 0.05, we conclude that the population mean of the two treatment groups are different.

```

**Step 3.** Our group also went to use Confidence Interval to see whether the population mean of the two treatment groups are the same 

```{r testing CI}
# mean, SD and sample size for normal group
x1 <- mean(df1[df1$treatment == "normal",2])
s1 <- sd(df1[df1$treatment == "normal",2])
n1 <- 31

# mean, SD and sample size for self group
x2 <- mean(df1[df1$treatment == "self",2])
s2 <- sd(df1[df1$treatment == "self",2])
n2 <- 31

# point estimate = normal mean score - self mean score
x1 - x2

# Slide 16: Standard Error

sp <- sqrt(((n1-1)*s1^2+(n2-1)*s2^2)/(n1+n2-2))
SE <- sp * sqrt(1/n1 + 1/n2)
SE

# Margin of error,qt is critical value of t-dist
moe <- qt(0.975,df=n1+n2-2) * SE
moe

# 95% Confidence interval = [point estimate - moe, point estimate + moe]
lowerCI <- (x1 - x2) - moe
upperCI <- (x1 - x2) + moe
c(lowerCI, upperCI) 

t.test(outcome~treatment, alternative = "two.sided", paired=FALSE, 
       var.equal=TRUE, data = df1)


result1 <- t.test(outcome~treatment, alternative = "two.sided", 
                  paired=FALSE, var.equal=TRUE, data = df1)
result1$conf.int
#since Confidence interval does not consist 0, we conclude that the population mean of the two treatment groups are different.

```

**Step 4.** After getting all the parameters, our group then use these parameters to build a simulation model.Our group has build 5 models
1.Base model,one queue to 10 normal counters
2.Base model,10 queue to 10 normal counters
3.10 queue to 10 self-checkout model
4.one queue to 10 mix model (trying to find the optimal number of normal and self counters)
5.10 queues to 2 normal and 8 self-checkout model.

```{r base model one queue to 10 normal counters}
library(simmer)
library(simmer.plot)
library(triangle)
library(scales)
set.seed(1)
Type1_wanderer <- function() rtriangle(1, 5, 10,8 ) #rdy to eat meal
Type2_wanderer <- function() rtriangle(1, 10, 15, 13) #small purchase,immediate use
Type3_wanderer <- function() rtriangle(1, 15, 25, 20) #for trips/gathering
Type4_wanderer <- function() rtriangle(1, 25, 45, 30) #Stocking groceries
Type5_wanderer <- function() rtriangle(1, 5, 45, 20) #others
Task_duration_normal <- function() rnorm(n = 1,mean=mean,sd=sd)
rep<- function() {
Customer <-
  trajectory("Customer") %>%
          branch(function() sample(c(1,2,3,4,5), size=1, prob=c(0.15,0.37,0.11,0.35,0.02)),
              continue =FALSE,
              trajectory() %>%
                set_attribute("type",1) %>%
                timeout(Type1_wanderer()) %>%
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),
              
              trajectory() %>%
                set_attribute("type",2) %>%
                timeout(Type2_wanderer()) %>%
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),
              
              trajectory() %>% 
                set_attribute("type",3) %>%
                timeout(Type3_wanderer()) %>%
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),
              
              trajectory() %>%
                set_attribute("type",4) %>%
                timeout(Type4_wanderer()) %>%
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),

              trajectory() %>%
                set_attribute("type",5) %>%
                timeout(Type5_wanderer()) %>%
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal")
              
           )

plot(Customer)
NTUC <-
  simmer("NTUC") %>%
  add_resource("Normal", capacity = 10) %>%
  add_generator("Customer", Customer,to(120,function() rexp(n = 1,rate=lambda)), 
                 mon = 2)%>% 
  run %>% wrap() #120 minutes
}

set.seed(1)
env <- replicate(20, rep())

mon_arrivals <- get_mon_arrivals(env)
mon_resources<- get_mon_resources(env)

mon_arrivals %>% 
  mutate(wait_time = end_time - start_time - activity_time)  %>%
  group_by(replication) %>%
  summarise(mean_wait_time = mean(wait_time)) %>%
  dplyr::select(mean_wait_time) %>% 
  unlist() %>% as.vector() %>% mean

mon_resources %>%
  group_by(replication) %>%
  summarise(mean_queue_length = mean(queue)) %>%
  dplyr::select(mean_queue_length) %>% 
  unlist() %>% as.vector() %>% mean

plot(mon_resources, metric="utilization")


```

Next we have Base model 10 queues to 10 normal counter
```{r Base model 10 queues to 10 normal counter}
library(simmer)
library(simmer.plot)
library(triangle)
library(scales)
library(dplyr)
set.seed(1)
Type1_wanderer <- function() rtriangle(1, 5, 10,8 ) #rdy to eat meal
Type2_wanderer <- function() rtriangle(1, 10, 15, 13) #small purchase,immediate use
Type3_wanderer <- function() rtriangle(1, 15, 25, 20) #for trips/gathering
Type4_wanderer <- function() rtriangle(1, 25, 45, 30) #Stocking groceries
Type5_wanderer <- function() rtriangle(1, 5, 45, 20) #others
Task_duration_normal <- function() rnorm(n = 1,mean=mean,sd=sd)


rep<- function() {
Customer <-
  trajectory("Customer") %>%
          branch(function() sample(c(1,2,3,4,5), size=1, prob=c(0.15,0.37,0.11,0.35,0.02)),
              continue =FALSE,
              trajectory() %>%
                set_attribute("type",1) %>%
                timeout(Type1_wanderer()) %>%
                
                #seize("Normal") %>%
                
                simmer::select(c("Normal 1","Normal 2","Normal 3","Normal 4","Normal 5","Normal 6","Normal 7","Normal 8","Normal 9","Normal 10"),
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                #release("Normal")%>%
                release_selected(),
              
              trajectory() %>%
                set_attribute("type",2) %>%
                timeout(Type2_wanderer()) %>%
                simmer::select(c("Normal 1","Normal 2","Normal 3","Normal 4","Normal 5","Normal 6","Normal 7","Normal 8","Normal 9","Normal 10"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                #release("Normal")%>%
                release_selected(),
              
              trajectory() %>% 
                set_attribute("type",3) %>%
                timeout(Type3_wanderer()) %>%
                simmer::select(c("Normal 1","Normal 2","Normal 3","Normal 4","Normal 5","Normal 6","Normal 7","Normal 8","Normal 9","Normal 10"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                #release("Normal")%>%
                release_selected(),
              
              trajectory() %>%
                set_attribute("type",4) %>%
                timeout(Type4_wanderer()) %>%
                simmer::select(c("Normal 1","Normal 2","Normal 3","Normal 4","Normal 5","Normal 6","Normal 7","Normal 8","Normal 9","Normal 10"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                #release("Normal")%>%
                release_selected(),

              trajectory() %>%
                set_attribute("type",5) %>%
                timeout(Type5_wanderer()) %>%
                simmer::select(c("Normal 1","Normal 2","Normal 3","Normal 4","Normal 5","Normal 6","Normal 7","Normal 8","Normal 9","Normal 10"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                #release("Normal")%>%
                release_selected()
              
           )

plot(Customer)
NTUC <-
  simmer("NTUC") %>%
  add_resource("Normal 1", capacity = 1) %>%
  add_resource("Normal 2", capacity = 1) %>%
  add_resource("Normal 3", capacity = 1) %>%
  add_resource("Normal 4", capacity = 1) %>%
  add_resource("Normal 5", capacity = 1) %>%
  add_resource("Normal 6", capacity = 1) %>%
  add_resource("Normal 7", capacity = 1) %>%
  add_resource("Normal 8", capacity = 1) %>%
  add_resource("Normal 9", capacity = 1) %>%
  add_resource("Normal 10", capacity = 1) %>%
  #add_resource("Normal", capacity = 10) %>%
  #add_generator("Customer", Customer,function() rpois(n = 1,lambda = poi_arrival$estimate[1]), 
                 #mon = 2)%>%
  add_generator("Customer", Customer,to(120,function() rexp(n = 1,rate=lambda)), 
                 mon = 2)%>% 
  run %>% wrap() #120 minutes
}

set.seed(1)
env <- replicate(20, rep())
mon_arrivals <- get_mon_arrivals(env)
mon_resources<- get_mon_resources(env)

mon_arrivals %>% 
  mutate(wait_time = end_time - start_time - activity_time)  %>%
  group_by(replication) %>%
  summarise(mean_wait_time = mean(wait_time)) %>%
  dplyr::select(mean_wait_time) %>% 
  unlist() %>% as.vector() %>% mean

mon_resources %>%
  group_by(replication) %>%
  summarise(mean_queue_length = mean(queue)) %>%
  dplyr::select(mean_queue_length) %>% 
  unlist() %>% as.vector() %>% mean

plot1 <- plot(mon_resources, items="queue")
df_resource <- plot1$data
df_resource %>% group_by(resource, replication) %>%
                summarise(mean_queue = tail(mean, n=1)) %>%
                group_by(resource) %>%
                summarise(mean_queue = mean(mean_queue))

plot(mon_resources, metric="utilization")

#conclude model 1 and model 2 roughly the same as the total mean waiting time and total mean queue length for the system is about the same.
```

Next we have the 1 queue to 10 self-check out model, similar to real life where self-checkout counters usually have one queue only.
```{r full self-check out model}
library(simmer)
library(simmer.plot)
library(triangle)
library(scales)
set.seed(1)
Type1_wanderer <- function() rtriangle(1, 5, 10,8 ) #rdy to eat meal
Type2_wanderer <- function() rtriangle(1, 10, 15, 13) #small purchase,immediate use
Type3_wanderer <- function() rtriangle(1, 15, 25, 20) #for trips/gathering
Type4_wanderer <- function() rtriangle(1, 25, 45, 30) #Stocking groceries
Type5_wanderer <- function() rtriangle(1, 5, 45, 20) #others
Task_duration_normal <- function() rnorm(n = 1,mean=mean,sd=sd)
Task_duration_self <- function() rnorm(n = 1,mean=mean1,sd=sd1)

rep2<-function(){
Customer <-
  trajectory("Customer") %>%
          branch(function() sample(c(1,2,3,4,5), size=1, prob=c(0.15,0.37,0.11,0.35,0.02)),
              continue =FALSE,
              trajectory() %>%
                set_attribute("type",1) %>%
                timeout(Type1_wanderer()) %>%
                seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self"),
              
              trajectory() %>%
                set_attribute("type",2) %>%
                timeout(Type2_wanderer()) %>%
                seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self"),
              
              trajectory() %>% 
                set_attribute("type",3) %>%
                timeout(Type3_wanderer()) %>%
                seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self"),
              
              trajectory() %>%
                set_attribute("type",4) %>%
                timeout(Type4_wanderer()) %>%
                seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self"),

              trajectory() %>%
                set_attribute("type",5) %>%
                timeout(Type5_wanderer()) %>%
                seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")
              
           )

plot(Customer)
NTUC <-
  simmer("NTUC") %>%
  add_resource("Self", capacity = 10) %>%
    add_generator("Customer", Customer,to(120,function() rexp(n = 1,rate=lambda)), 
                 mon = 2)%>% 
  run %>% wrap() #120 minutes
}

set.seed(1)
env1 <- replicate(20, rep2())

mon_arrivals <- get_mon_arrivals(env1)
mon_resources<- get_mon_resources(env1)

mon_arrivals %>% 
  mutate(wait_time = end_time - start_time - activity_time)  %>%
  group_by(replication) %>%
  summarise(mean_wait_time = mean(wait_time)) %>%
  dplyr::select(mean_wait_time) %>% 
  unlist() %>% as.vector() %>% mean

mon_resources %>%
  group_by(replication) %>%
  summarise(mean_queue_length = mean(queue)) %>%
  dplyr::select(mean_queue_length) %>% 
  unlist() %>% as.vector() %>% mean
plot(mon_resources, metric="utilization")
```

Next, we have mix model trying to find out optimal number of normal and self-checkout counters, using sapply function. Where this is one queue to many normal counters and one queue to many self-check out counters.
```{r mix model,to find out the optimal number of normal and self-checkout counters }
library(simmer)
library(simmer.plot)
library(triangle)
library(scales)
library(tidyverse)
set.seed(1)
Type1_wanderer <- function() rtriangle(1, 5, 10,8 ) #rdy to eat meal
Type2_wanderer <- function() rtriangle(1, 10, 15, 13) #small purchase,immediate use
Type3_wanderer <- function() rtriangle(1, 15, 25, 20) #for trips/gathering
Type4_wanderer <- function() rtriangle(1, 25, 45, 30) #Stocking groceries
Type5_wanderer <- function() rtriangle(1, 5, 45, 20) #others
Task_duration_normal <- function() rnorm(n = 1,mean=mean,sd=sd)
Task_duration_self <- function() rnorm(n = 1,mean=mean1,sd=sd1)
rep3<- function(cap) {
Customer <-
  trajectory("Customer") %>%
          branch(function() sample(c(1,2,3,4,5), size=1, prob=c(0.15,0.37,0.11,0.35,0.02)),
              continue =FALSE,
              trajectory() %>%
                set_attribute("type",1) %>%
                timeout(Type1_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(cap/10,(10-cap)/10)),
              continue = FALSE,
              trajectory() %>% 
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")),
              
              trajectory() %>%
                set_attribute("type",2) %>%
                timeout(Type2_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(cap/10,(10-cap)/10)),
              continue = FALSE,
              trajectory() %>% 
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")),
              
              trajectory() %>% 
                set_attribute("type",3) %>%
                timeout(Type3_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(cap/10,(10-cap)/10)),
              continue = FALSE,
              trajectory() %>% 
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")),
              
              trajectory() %>%
                set_attribute("type",4) %>%
                timeout(Type4_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(cap/10,(10-cap)/10)),
              continue = FALSE,
              trajectory() %>% 
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")),

              trajectory() %>%
                set_attribute("type",5) %>%
                timeout(Type5_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(cap/10,(10-cap)/10)),
              continue = FALSE,
              trajectory() %>% 
                seize("Normal") %>%
                timeout(Task_duration_normal()) %>%
                release("Normal"),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self"))
              
           )

plot(Customer)
NTUC <-
  simmer("NTUC") %>%
  add_resource("Normal", capacity = cap) %>%
  add_resource("Self", capacity = 10-cap) %>%
  add_generator("Customer", Customer,to(120,function() rexp(n = 1,rate=lambda)), 
                 mon = 2)%>% 
  run %>% wrap() #120 minutes
}

set.seed(1)
sapply(1:9, function(cap) {
  env3 <- replicate(20, rep3(cap))
  mon_arrivals <- get_mon_arrivals(env3)
  mon_resources<- get_mon_resources(env3)
  
  mon_arrivals %>% 
    mutate(wait_time = end_time - start_time - activity_time)  %>%
    group_by(replication) %>%
    summarise(mean_wait_time = mean(wait_time)) %>%
    dplyr::select(mean_wait_time) %>% 
    unlist() %>% as.vector() %>% mean  -> mean_wait_time
  
  mon_resources %>%
  group_by(replication) %>%
  summarise(mean_queue_length = mean(queue)) %>%
  dplyr::select(mean_queue_length) %>% 
  unlist() %>% as.vector() %>% mean -> mean_queue_length
  
  
  paste("The mean waiting time and mean queue length with ", cap, " normal counter and ",10-cap,"self-check out counter is ", mean_wait_time, mean_queue_length )
})

#conclude, under mix model, 2 normal and 8 self-checkout would be appropriate, as it has one of the lowest mean waiting time and mean queue length in the system.
```

Lastly,from the previous model we conclude that the optimal solution would be 1 queue to 8 self-checkout counters and 2 queues to 2 normal counters.As per real life, where usually have only 1 queue for self-checkout counters.
```{r half half model}
library(simmer)
library(simmer.plot)
library(triangle)
library(scales)
set.seed(1)
Type1_wanderer <- function() rtriangle(1, 5, 10,8 ) #rdy to eat meal
Type2_wanderer <- function() rtriangle(1, 10, 15, 13) #small purchase,immediate use
Type3_wanderer <- function() rtriangle(1, 15, 25, 20) #for trips/gathering
Type4_wanderer <- function() rtriangle(1, 25, 45, 30) #Stocking groceries
Type5_wanderer <- function() rtriangle(1, 5, 45, 20) #others
Task_duration_normal <- function() rnorm(n = 1,mean=mean,sd=sd)
Task_duration_self <- function() rnorm(n = 1,mean=mean1,sd=sd1)

rep3<- function() {
Customer <-
  trajectory("Customer") %>%
          branch(function() sample(c(1,2,3,4,5), size=1, prob=c(0.15,0.37,0.11,0.35,0.02)),
              continue =FALSE,
              trajectory() %>%
                set_attribute("type",1) %>%
                timeout(Type1_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(0.2,0.8)),
              continue = FALSE,
              trajectory() %>% 
               simmer::select(c("Normal 1","Normal 2"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                release_selected(),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")),
              
              trajectory() %>%
                set_attribute("type",2) %>%
                timeout(Type2_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(0.2,0.8)),
              continue = FALSE,
              trajectory() %>% 
                simmer::select(c("Normal 1","Normal 2"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                release_selected(),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")),
              
              trajectory() %>% 
                set_attribute("type",3) %>%
                timeout(Type3_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(0.2,0.8)),
              continue = FALSE,
              trajectory() %>% 
                simmer::select(c("Normal 1","Normal 2"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                release_selected(),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")),
              
              trajectory() %>%
                set_attribute("type",4) %>%
                timeout(Type4_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(0.2,0.8)),
              continue = FALSE,
              trajectory() %>% 
                simmer::select(c("Normal 1","Normal 2"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                release_selected(),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self")),

              trajectory() %>%
                set_attribute("type",5) %>%
                timeout(Type5_wanderer()) %>%
                branch(function() sample(c(1,2), size=1, prob=c(0.2,0.8)),
              continue = FALSE,
              trajectory() %>% 
                simmer::select(c("Normal 1","Normal 2"), 
                policy = "shortest-queue") %>%
                seize_selected() %>%
                timeout(Task_duration_normal()) %>%
                release_selected(),
              trajectory() %>%
              seize("Self") %>%
                timeout(Task_duration_self()) %>%
                release("Self"))
              
           )

plot(Customer)
NTUC <-
  simmer("NTUC") %>%
  add_resource("Self", capacity = 8) %>%
  add_resource("Normal 1", capacity = 1) %>%
  add_resource("Normal 2", capacity = 1) %>%

  add_generator("Customer", Customer,to(120,function() rexp(n = 1,rate=lambda)), 
                 mon = 2)%>% 
  run %>% wrap() #120 minutes
}

#base on the results above, we conclude that 5 normal and 5 mix would be the best for the NTUC as it has the lowest mean waiting time and mean queue length.
set.seed(1)
env3 <- replicate(20, rep3())
  mon_arrivals <- get_mon_arrivals(env3)
  mon_resources<- get_mon_resources(env3)
  
  mon_arrivals %>% 
    mutate(wait_time = end_time - start_time - activity_time)  %>%
    group_by(replication) %>%
    summarise(mean_wait_time = mean(wait_time)) %>%
    dplyr::select(mean_wait_time) %>% 
    unlist() %>% as.vector() %>% mean  -> mean_wait_time
  
  mon_resources %>%
  group_by(replication) %>%
  summarise(mean_queue_length = mean(queue)) %>%
  dplyr::select(mean_queue_length) %>% 
  unlist() %>% as.vector() %>% mean -> mean_queue_length
  
  
mean_wait_time
mean_queue_length
plot(mon_resources, metric="utilization") 
  
```

Conclusion: 

Even though 10 self-check out counter has the lowest mean waiting time and mean queue length.Some elderly who are not familiar with self-check out system would still prefer having normal counters.Moreover, some people that buys a lot of food would maybe prefer someone to help them pack.Therefore, still prefer normal counter.Therefore, our group do not recommend fully self-check out system.Thus,our group concluded that 8 self-checkout counters and 2 normal counters would be optimal as it has one of the lowest mean waiting time and lowest mean queue length. While also satisfy those customers that still prefer the normal counters.

model 5(2 queues to 2 normal counters and 1 queue to 8 self-checkout):
mean waiting time = 5.18, mean queue length = 4.12, total queue in system=4.12X3=12.36 (multiple 3 because 3 queues)

Base model 2 (10 queues to 10 normal counters) :
mean waiting time = 10.72 min, mean queue length = 3.18, total queue in system= 3.18X10=31.8(multiple 10 because 10 queues)

Therefore, mean waiting time has improved around 50% and around 60% for the total queue length in system. Which is a good improvement. :)
